A systematic search for transiting planets in the \KT\ data

### 2015-02-13 ms.tex
tinytweak

We have searched the \KT\ Campaign~1 data set for exoplanet transit signals.
Our search is novel because it includes a very flexible systematics model,
which is fit simultaneously with the exoplanet signals of interest, and
marginalized out.
By this method, we find XXX new exoplanets, which we have vetted by ZZZ
method and characterized by probabilistic modeling.
The candidates are listed in \dfmtodo{some table} and
posterior distributions of planet candidate properties are available at
\dfmtodo{thisurl}.

>>>>

We have searched the \KT\ Campaign~1 data set for exoplanet transit signals.
Our search is novel because it includes a very flexible systematics model,
which is fit simultaneously with the exoplanet signals of interest (and
marginalized out).
By this method, we find XXX new exoplanets, which we have vetted by ZZZ
method and characterized by probabilistic modeling.
The candidates are listed in \dfmtodo{some table} and
posterior distributions of planet candidate properties are available at
\dfmtodo{thisurl}.
